Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-14 analysis/paper/paper.Rmd
clean up inclusions in output

```{r, setup, echo=FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "tidyr",
  "tools"
)

# install packages if needed
install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org",
                 dependencies = TRUE)

# load packages for use in knitting Rmd
invisible(lapply(packages,
                 library,
                 character.only = TRUE))

library("Reproducibility.in.Plant.Pathology")

>>>>

```{r, setup, echo=FALSE, message=FALSE, include=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "rstan",
  "tidyr",
  "tools"
)

# install packages if needed
install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org",
                 dependencies = TRUE)
# load packages for use in knitting Rmd
invisible(lapply(packages,
                 library,
                 character.only = TRUE))
library("Reproducibility.in.Plant.Pathology")
